\documentclass[../main]{subfiles}

\begin{document}
\chapter*{Preface to the new Typesetting}
\addcontentsline{toc}{chapter}{Editor's Preface}

The book was TeX'd up by the Texromancers, a latexing group. The credits for the typesetting of this book go to:  Aareyan Manzoor, Jonas Hardt, Evelyn Koo, Yohan Wittgenstein, Grisha Taroyan and others.

Here is a link to a dyslexic friendly version of the book:
\url{https://aareyanmanzoor.github.io/assets/books/homotopical-algebra-dyslexic.pdf} . Here is a link to our \LaTeX : \url{https://github.com/AareyanManzoor/Quillen-Homotopical-Algebra}

We added citations and references with hyperlinks. References to e.g. theorems/lemmas in the book are in blue, while citations to the bibliography is
in red. The bibliography also has URLs now, for easy access. Some of the books
in the bibliography had newer editions, so we went with those.

We also added a small index. This is minimalist as of now, if the reader feels more words should be added to it, please let us know. Also please report typos or anything else to us, readers taking the time to help the proofreading is appreciated. This can be reported at our website: \url{https://aareyanmanzoor.github.io/Texromancers.html}.

We changed some notations, particularly for the name of categories. (sets) is now $\mathbf{Set}$ for example. Underlining is also a relic of the typewritter era, so those were replaced with bolded text, same for category names. For example category $\xunderline{C}$ in the original book is now $\mathbf{C}$.

All diagrams are redrawn in tikz or tikzcd.
\end{document}